Pattern Avoidance

### 2014-11-07 project2/paper/paper.tex
in fact

In fact, note that any permutation $\pi\in T_n$ which satisfies this condition - for all $i\leq n$, all the even integers to the right of $i$ and less than $i$ are in decreasing order - is in fact a permutation in $A$. Suppose for the sake of contradiction $\pi$ had a subsequence $x, y, z$ following the pattern 312 (so in particular $x>z>y$). Since it is in $T_n$, by Lemma  \ref{tn_avoidance} $y$ and $z$ must be even. Then by the assumed property of $\pi$ we must have $y>z$, a contradiction; hence such a subsequence cannot exist, and so $\pi$ avoids 312. We have a similar result for $B$: $B$ is precisely the set of permutations $\pi\in T_n$ satisfying the condition that, for all $i\leq n$, all even integers to the right of $i$ and less than $i$ are in decreasing order.

>>>>

In fact, note that any permutation $\pi\in T_n$ which satisfies this condition - for all $i\leq n$, all the even integers to the right of $i$ and less than $i$ are in decreasing order - is a permutation in $A$. Suppose for the sake of contradiction $\pi$ had a subsequence $x, y, z$ following the pattern 312 (so in particular $x>z>y$). Since it is in $T_n$, by Lemma  \ref{tn_avoidance} $y$ and $z$ must be even. Then by the assumed property of $\pi$ we must have $y>z$, a contradiction; hence such a subsequence cannot exist, and so $\pi$ avoids 312. We have a similar result for $B$: $B$ is precisely the set of permutations $\pi\in T_n$ satisfying the condition that, for all $i\leq n$, all even integers to the right of $i$ and less than $i$ are in decreasing order.
